% ═══════════════════════════════════════════════════════════════════════════════
% Resume V1 — Backend Product Engineer
% Target: Naukri, LinkedIn, Direct product company applications
% Emphasis: Node.js, Express, REST APIs, System Design, Linux, Production Ops
% ═══════════════════════════════════════════════════════════════════════════════
\documentclass[10pt, a4paper]{article}

% ── Encoding & Fonts ──────────────────────────────────────────────────────────
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% ── Page Geometry ─────────────────────────────────────────────────────────────
\usepackage[
  top=0.3in,
  bottom=0.3in,
  left=0.45in,
  right=0.45in
]{geometry}

% ── Packages ──────────────────────────────────────────────────────────────────
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}

% ── Colors ────────────────────────────────────────────────────────────────────
\definecolor{linkblue}{HTML}{1A5276}
\definecolor{heading}{HTML}{1B2631}

% ── Hyperlink Setup ───────────────────────────────────────────────────────────
\hypersetup{
  colorlinks=true,
  urlcolor=linkblue,
  pdfauthor={Vaibhav Kumar},
  pdftitle={Vaibhav Kumar -- Backend Product Engineer},
}

% ── Section Formatting ────────────────────────────────────────────────────────
\titleformat{\section}
  {\normalsize\bfseries\color{heading}}
  {}{0em}{\MakeUppercase}
  [\vspace{-6pt}\textcolor{heading}{\rule{\textwidth}{0.5pt}}\vspace{-4pt}]

\titlespacing*{\section}{0pt}{6pt}{3pt}

% ── List Configuration ────────────────────────────────────────────────────────
\setlist[itemize]{
  nosep,
  left=0pt .. 12pt,
  label=\textbullet,
  itemsep=0.5pt,
  parsep=0pt,
  topsep=1pt,
}

% ── Spacing ───────────────────────────────────────────────────────────────────
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagestyle{empty}

% ── Custom Commands ───────────────────────────────────────────────────────────
\newcommand{\entryHeading}[4]{%
  \textbf{#1} \hfill \textit{#2} \\[-1pt]
  \textit{#3} \hfill #4 \vspace{1pt}%
}

\newcommand{\projectTitle}[2]{%
  \textbf{#1} \hfill \textit{#2}%
}

% ══════════════════════════════════════════════════════════════════════════════
\begin{document}

% ── Header ────────────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries Vaibhav Kumar} \\[3pt]
  {\small
    India \enspace$|$\enspace
    \href{mailto:shanuv000@gmail.com}{shanuv000@gmail.com} \enspace$|$\enspace
    \href{https://linkedin.com/in/shanuv000}{linkedin.com/in/shanuv000} \enspace$|$\enspace
    \href{https://github.com/shanuv000}{github.com/shanuv000}
  }
\end{center}

\vspace{-4pt}

% ── Summary ───────────────────────────────────────────────────────────────────
\section{Summary}
\vspace{-1pt}
Backend-focused product engineer with 2+ years
building production APIs, scalable architectures, and deployment infrastructure.
Owns systems end-to-end---from Express API design and MongoDB modeling
to Nginx configuration, SSL, PM2 process management, and production monitoring.
Integrates applied AI into backend workflows pragmatically.

% ── Technical Skills ──────────────────────────────────────────────────────────
\section{Technical Skills}
\vspace{-1pt}

\textbf{Backend \& APIs:}
  Node.js, Express.js, REST API Design, JWT Authentication, RBAC,
  System Design, WebSockets \\[1pt]
\textbf{Infrastructure:}
  Linux VPS Administration, Nginx, PM2, SSL/TLS,
  UFW Firewall, CI/CD, Vercel, Zero-Downtime Deploys \\[1pt]
\textbf{Databases:}
  MongoDB, SQLite, Firebase Realtime DB,
  GraphQL (Hygraph / Apollo Client) \\[1pt]
\textbf{AI \& Data:}
  Python, Pandas, NumPy, LLM API Integration,
  LangGraph Multi-Agent Systems \\[1pt]
\textbf{Frontend:}
  React.js, Next.js 14, Tailwind CSS, SSG/ISR \\[1pt]
\textbf{Tools:}
  Git, Docker, Sentry, Cloudinary, Google Analytics

% ── Experience ────────────────────────────────────────────────────────────────
\section{Experience}

\entryHeading
  {Software Engineer (Independent)}
  {2023 -- Present}
  {Backend Systems \& Production Infrastructure}
  {Remote, India}
\begin{itemize}
  \item Design and deploy production Node.js/Express APIs
    with JWT authentication, role-based access control,
    input validation, and rate limiting---serving real users at scale.
  \item Administer Linux VPS infrastructure:
    Nginx reverse proxy, PM2 clustering, SSL automation,
    UFW firewall hardening, and zero-downtime deployment pipelines.
  \item Architect MongoDB data models and query pipelines
    optimized for read-heavy workloads with proper indexing and aggregation.
  \item Integrate LLM APIs into backend services
    with retry logic, validation layers, and fallback mechanisms
    ensuring production reliability.
\end{itemize}

% ── Projects ──────────────────────────────────────────────────────────────────
\section{Projects}

% ── urTechy (lead project for V1) ──
\projectTitle
  {urTechy Blogs --- Production Content Platform}
  {\href{https://blog.urtechy.com}{blog.urtechy.com}}
\begin{itemize}
  \item Built and operate a Next.js 14 platform
    with SSG + ISR (60--300s revalidation),
    sub-2s page loads via Cloudinary optimization
    and Apollo Client caching layer.
  \item Designed 25+ API routes:
    Hygraph GraphQL proxy, Firebase comment system
    with multi-layer fallbacks, webhook integrations,
    and cricket score aggregation endpoints.
  \item Implemented production SEO:
    JSON-LD structured data, dynamic XML sitemaps,
    news sitemaps, and per-page meta optimization.
  \item Deployed on Vercel (Mumbai) with custom cache headers,
    standalone output, chunk splitting, and Sentry monitoring.
\end{itemize}

\vspace{3pt}

% ── Goldfish (secondary in V1) ──
\projectTitle
  {Goldfish --- LLM-Powered Trading System}
  {\href{https://github.com/shanuv000}{GitHub}}
\begin{itemize}
  \item Built multi-agent execution system using LangGraph
    with specialized agents collaborating through orchestrated graph
    and human-in-the-loop validation before live orders.
  \item Engineered execution bridge interfacing with Upstox broker API:
    order placement, position tracking,
    real-time P\&L, and automatic SL/TP enforcement.
  \item Implemented risk engine
    with kill switches, exposure limits, drawdown caps,
    and circuit breakers; SQLite audit trail for every decision.
\end{itemize}

\vspace{3pt}

% ── SportsPulse ──
\projectTitle
  {SportsPulse --- AI Sports Analytics}
  {\href{https://github.com/shanuv000}{GitHub}}
\begin{itemize}
  \item Developed MERN-stack platform
    with real-time data pipelines and AI-generated insights
    served through authenticated RESTful APIs.
  \item Built JWT-secured endpoints with RBAC, rate limiting,
    and validation middleware; sub-200ms P95 response times.
\end{itemize}

% ── Education ─────────────────────────────────────────────────────────────────
\section{Education}

\textbf{Master of Computer Applications (AI \& ML)} \hfill 2023 -- 2025 \\[-1pt]
Amity University Online \hfill CGPA: 8.30 / 10 \\[3pt]
\textbf{Bachelor of Science in Information Technology} \hfill 2019 -- 2022 \\[-1pt]
Ram Krishna Dwarika College, Patna

\end{document}
