% ═══════════════════════════════════════════════════════════════════════════════
% Resume V2 — Applied AI Systems Engineer
% Target: Wellfound, AI startups, YC-backed companies, early-stage
% Emphasis: LangGraph, multi-agent orchestration, risk engines, system invariants
% ═══════════════════════════════════════════════════════════════════════════════
\documentclass[10pt, a4paper]{article}

% ── Encoding & Fonts ──────────────────────────────────────────────────────────
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% ── Page Geometry ─────────────────────────────────────────────────────────────
\usepackage[
  top=0.3in,
  bottom=0.3in,
  left=0.45in,
  right=0.45in
]{geometry}

% ── Packages ──────────────────────────────────────────────────────────────────
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}

% ── Colors ────────────────────────────────────────────────────────────────────
\definecolor{linkblue}{HTML}{1A5276}
\definecolor{heading}{HTML}{1B2631}

% ── Hyperlink Setup ───────────────────────────────────────────────────────────
\hypersetup{
  colorlinks=true,
  urlcolor=linkblue,
  pdfauthor={Vaibhav Kumar},
  pdftitle={Vaibhav Kumar -- Applied AI Systems Engineer},
}

% ── Section Formatting ────────────────────────────────────────────────────────
\titleformat{\section}
  {\normalsize\bfseries\color{heading}}
  {}{0em}{\MakeUppercase}
  [\vspace{-6pt}\textcolor{heading}{\rule{\textwidth}{0.5pt}}\vspace{-4pt}]

\titlespacing*{\section}{0pt}{6pt}{3pt}

% ── List Configuration ────────────────────────────────────────────────────────
\setlist[itemize]{
  nosep,
  left=0pt .. 12pt,
  label=\textbullet,
  itemsep=0.5pt,
  parsep=0pt,
  topsep=1pt,
}

% ── Spacing ───────────────────────────────────────────────────────────────────
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagestyle{empty}

% ── Custom Commands ───────────────────────────────────────────────────────────
\newcommand{\entryHeading}[4]{%
  \textbf{#1} \hfill \textit{#2} \\[-1pt]
  \textit{#3} \hfill #4 \vspace{1pt}%
}

\newcommand{\projectTitle}[2]{%
  \textbf{#1} \hfill \textit{#2}%
}

% ══════════════════════════════════════════════════════════════════════════════
\begin{document}

% ── Header ────────────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries Vaibhav Kumar} \\[3pt]
  {\small
    India \enspace$|$\enspace
    \href{mailto:shanuv000@gmail.com}{shanuv000@gmail.com} \enspace$|$\enspace
    \href{https://linkedin.com/in/shanuv000}{linkedin.com/in/shanuv000} \enspace$|$\enspace
    \href{https://github.com/shanuv000}{github.com/shanuv000}
  }
\end{center}

\vspace{-4pt}

% ── Summary ───────────────────────────────────────────────────────────────────
\section{Summary}
\vspace{-1pt}
Applied AI systems engineer with 2+ years
building production-grade multi-agent architectures,
risk-controlled execution systems, and scalable backend infrastructure.
Designs AI pipelines with system invariants, kill switches,
and validation gates---ensuring reliability before live deployment.
Strong backend foundation across Node.js, Python, and Linux infrastructure.

% ── Technical Skills ──────────────────────────────────────────────────────────
\section{Technical Skills}
\vspace{-1pt}

\textbf{AI \& Agents:}
  LangGraph Multi-Agent Orchestration, LLM API Integration,
  Python, Pandas, NumPy, Risk-Controlled Execution Systems \\[1pt]
\textbf{Backend \& APIs:}
  Node.js, Express.js, REST API Design, JWT Authentication,
  RBAC, System Design \\[1pt]
\textbf{Infrastructure:}
  Linux VPS, Nginx, PM2, SSL/TLS, Firewall Hardening,
  CI/CD, Cron Automation, Vercel \\[1pt]
\textbf{Databases:}
  MongoDB, SQLite, Firebase Realtime DB,
  GraphQL (Hygraph / Apollo Client) \\[1pt]
\textbf{Frontend:}
  React.js, Next.js 14, Tailwind CSS, SSG/ISR \\[1pt]
\textbf{Tools:}
  Git, Docker, Sentry, Cloudinary

% ── Projects (Goldfish leads in V2) ──────────────────────────────────────────
\section{Projects}

% ── Goldfish (primary in V2) ──
\projectTitle
  {Goldfish --- Multi-Agent Algorithmic Trading System}
  {\href{https://github.com/shanuv000}{GitHub}}
\begin{itemize}
  \item Architected a \textbf{LangGraph} multi-agent system
    where specialized agents (market analyst, risk manager, executor)
    collaborate through an orchestrated state graph
    with human-in-the-loop validation before live order placement.
  \item Built production execution bridge
    interfacing with Upstox broker API---handles order placement,
    position tracking, real-time P\&L computation,
    and automatic stop-loss/take-profit enforcement.
  \item Engineered risk engine enforcing system invariants:
    configurable kill switches, per-trade exposure limits,
    daily drawdown caps, and circuit breakers
    that halt all execution on anomalous behavior.
  \item Implemented SQLite-based trade journaling
    with full audit trail---every signal, agent rationale,
    and execution outcome persisted
    for post-market analysis and strategy refinement.
  \item Deployed autonomous paper trading pipeline
    on Linux VPS with cron-scheduled validation cycles;
    50+ cycles completed before any live capital deployment.
  \item Designed validation gate architecture:
    confidence thresholds, win-rate requirements,
    and drawdown limits must pass before system promotion to live trading.
\end{itemize}

\vspace{3pt}

% ── urTechy (secondary in V2) ──
\projectTitle
  {urTechy Blogs --- Production Content Platform}
  {\href{https://blog.urtechy.com}{blog.urtechy.com}}
\begin{itemize}
  \item Built and operate a Next.js 14 platform
    with SSG + ISR, sub-2s loads via Cloudinary optimization,
    Apollo caching, and 25+ API proxy routes.
  \item Designed API layer handling
    GraphQL proxying, Firebase comments with fallback chains,
    webhook integrations, and real-time data aggregation.
  \item Deployed on Vercel (Mumbai) with cache headers,
    standalone output, Sentry monitoring,
    and JSON-LD structured data for SEO.
\end{itemize}

\vspace{3pt}

% ── SportsPulse ──
\projectTitle
  {SportsPulse --- AI Sports Analytics}
  {\href{https://github.com/shanuv000}{GitHub}}
\begin{itemize}
  \item Developed MERN-stack analytics platform with real-time data pipelines
    and JWT/RBAC-secured REST APIs delivering AI-driven insights.
\end{itemize}

% ── Experience ────────────────────────────────────────────────────────────────
\section{Experience}

\entryHeading
  {Software Engineer (Independent)}
  {2023 -- Present}
  {Applied AI Systems \& Backend Infrastructure}
  {Remote, India}
\begin{itemize}
  \item Build and deploy multi-agent AI systems
    with production guardrails---validation gates, kill switches,
    and fallback mechanisms ensuring reliability under real conditions.
  \item Design and own backend services end-to-end:
    API architecture, database modeling, deployment,
    monitoring, and incident response.
  \item Administer Linux VPS infrastructure:
    Nginx, PM2, SSL automation, firewall hardening,
    and cron-based autonomous execution pipelines.
\end{itemize}

% ── Education ─────────────────────────────────────────────────────────────────
\section{Education}

\textbf{Master of Computer Applications (AI \& ML)} \hfill 2023 -- 2025 \\[-1pt]
Amity University Online \hfill CGPA: 8.30 / 10 \\[3pt]
\textbf{Bachelor of Science in Information Technology} \hfill 2019 -- 2022 \\[-1pt]
Ram Krishna Dwarika College, Patna

\end{document}
