\documentclass[10pt, a4paper]{article}

% ── Encoding & Fonts ──────────────────────────────────────────────────────────
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% ── Page Geometry ─────────────────────────────────────────────────────────────
\usepackage[top=0.3in, bottom=0.3in, left=0.45in, right=0.45in]{geometry}

% ── Packages ──────────────────────────────────────────────────────────────────
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}

% ── Colors ────────────────────────────────────────────────────────────────────
\definecolor{linkblue}{HTML}{1A5276}
\definecolor{rulecolor}{HTML}{2C3E50}

% ── Hyperlink Setup ───────────────────────────────────────────────────────────
\hypersetup{
    colorlinks=true,
    urlcolor=linkblue,
    pdfauthor={Vaibhav Kumar},
    pdftitle={Vaibhav Kumar - Backend and Applied AI Engineer},
}

% ── Section Formatting (uppercase titles instead of \scshape to avoid font warning) ──
\titleformat{\section}
  {\normalsize\bfseries\color{rulecolor}}
  {}{0em}{\MakeUppercase}
  [\vspace{-6pt}\textcolor{rulecolor}{\rule{\textwidth}{0.5pt}}\vspace{-4pt}]

\titlespacing*{\section}{0pt}{6pt}{3pt}

% ── List Configuration ────────────────────────────────────────────────────────
\setlist[itemize]{
  nosep,
  left=0pt .. 12pt,
  label=\textbullet,
  itemsep=0.5pt,
  parsep=0pt,
  topsep=1pt,
}

% ── Paragraph & Spacing ──────────────────────────────────────────────────────
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\pagestyle{empty}

% ── Custom Commands ───────────────────────────────────────────────────────────
\newcommand{\resumeHeading}[4]{%
  \textbf{#1} \hfill \textit{#2} \\[-1pt]
  \textit{#3} \hfill #4 \vspace{1pt}%
}

\newcommand{\projectHeading}[2]{%
  \textbf{#1} \hfill \textit{#2}%
}

% ══════════════════════════════════════════════════════════════════════════════
\begin{document}

% ── Header ────────────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries Vaibhav Kumar} \\[3pt]
  {\small
  India \enspace$\vert$\enspace
  \href{mailto:shanuv000@gmail.com}{shanuv000@gmail.com} \enspace$\vert$\enspace
  \href{https://linkedin.com/in/shanuv000}{linkedin.com/in/shanuv000} \enspace$\vert$\enspace
  \href{https://github.com/shanuv000}{github.com/shanuv000}}
\end{center}

\vspace{-4pt}

% ── Summary ───────────────────────────────────────────────────────────────────
\section{Summary}
\vspace{-1pt}
Backend-first engineer with 2+ years building production systems, scalable APIs, and applied AI integrations.
Owns full deployment lifecycle on Linux infrastructure---API design, database modeling, Nginx, SSL, and process management. Builds systems that run in production, not prototypes in notebooks.

% ── Technical Skills ──────────────────────────────────────────────────────────
\section{Technical Skills}
\vspace{-1pt}

\textbf{Backend \& APIs:} Node.js, Express.js, REST API Design, JWT Auth, RBAC, System Design \\[1pt]
\textbf{Infrastructure:} Linux VPS, Nginx, PM2, SSL/TLS, Firewall Hardening, CI/CD, Vercel \\[1pt]
\textbf{Databases:} MongoDB, SQLite, Firebase, GraphQL (Hygraph / Apollo Client) \\[1pt]
\textbf{AI \& Data:} Python, Pandas, NumPy, LLM APIs, LangGraph Multi-Agent Orchestration \\[1pt]
\textbf{Frontend:} React.js, Next.js 14, Tailwind CSS, Framer Motion, SSG/ISR \\[1pt]
\textbf{Tools:} Git, Docker, Sentry, Google Analytics, Cloudinary

% ── Projects ──────────────────────────────────────────────────────────────────
\section{Projects}
\vspace{-1pt}

% ── Goldfish ──
\projectHeading{Goldfish --- LLM-Powered Algorithmic Trading System}{\href{https://github.com/shanuv000}{GitHub}}
\begin{itemize}
  \item Architected a multi-agent trading engine using \textbf{LangGraph}---specialized agents (analyst, risk manager, executor) collaborate through an orchestrated graph with human-in-the-loop validation before live orders.
  \item Built execution bridge interfacing with Upstox broker API: order placement, position tracking, real-time P\&L, and automatic SL/TP enforcement.
  \item Engineered risk engine with kill switches, per-trade exposure limits, daily drawdown caps, and circuit breakers that halt trading on anomalous behavior.
  \item Implemented SQLite trade journaling with full audit trail---every signal, rationale, and outcome persisted for post-market analysis.
  \item Deployed paper trading pipeline with cron-scheduled autonomous cycles on Linux VPS; 50+ validation cycles before live capital deployment.
\end{itemize}

\vspace{3pt}

% ── urTechy ──
\projectHeading{urTechy Blogs --- Production Content Platform}{\href{https://blog.urtechy.com}{blog.urtechy.com}}
\begin{itemize}
  \item Built and operate a Next.js 14 platform with SSG + ISR (60--300s revalidation), sub-2s loads via Cloudinary optimization and Apollo Client caching.
  \item Designed API proxy layer (25+ routes): Hygraph GraphQL proxy, Firebase comments with multi-layer fallbacks, Telegram webhooks.
  \item Implemented SEO infrastructure: JSON-LD structured data (Article, Breadcrumb, Organization), dynamic sitemaps, and per-page meta optimization.
  \item Engineered 1600-line rich text renderer transforming Hygraph CMS into React---handles social embeds, code blocks, tables.
  \item Deployed on Vercel (Mumbai) with cache headers, standalone output, chunk splitting, and Sentry error tracking.
\end{itemize}

\vspace{3pt}

% ── SportsPulse ──
\projectHeading{SportsPulse --- AI-Driven Sports Analytics Platform}{\href{https://github.com/shanuv000}{GitHub}}
\begin{itemize}
  \item Developed MERN-stack platform with real-time data pipelines ingesting live sports APIs and serving AI-generated insights via RESTful backend.
  \item Built JWT-authenticated APIs with RBAC, rate limiting, and validation middleware; sub-200ms response times under concurrent load.
\end{itemize}

% ── Experience ────────────────────────────────────────────────────────────────
\section{Experience}

\resumeHeading{Independent Software Engineer}{2023 -- Present}{Backend Systems, Production Infrastructure, Applied AI}{Remote, India}
\begin{itemize}
  \item Own end-to-end delivery: architecture design, implementation, deployment, monitoring, and incident response for production services.
  \item Manage Linux VPS infrastructure---Nginx reverse proxy, PM2 process management, SSL automation, firewall rules, zero-downtime deploys.
  \item Integrate LLM APIs and multi-agent systems into production workflows with guardrails, validation layers, and fallback mechanisms.
\end{itemize}

% ── Education ─────────────────────────────────────────────────────────────────
\section{Education}

\textbf{Master of Computer Applications (AI \& ML)} \hfill 2023 -- 2025 \\[-1pt]
Amity University Online \hfill CGPA: 8.30 / 10 \\[3pt]
\textbf{Bachelor of Science in Information Technology} \hfill 2019 -- 2022 \\[-1pt]
Ram Krishna Dwarika College, Patna

\end{document}
